---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
### dgutils
My utility functions package, complete with documentation.  There are
 aliases for these bash commands: `cd`, `pwd`, and `env`.

The `note` function to record comments in the history file. Handy to record some
thoughts immediately after the execution of some code.  Here's an example from
my first time using [directlabels](http://directlabels.r-forge.r-project.org/):
```{r note command, eval=FALSE}
note("Plot labels have wrong color - try explicit aes() for geom_dl")
```
added this to the history file:


`theme_dg` gathers up the standard changes I make to ggplot's `theme_bw`.

Install with this R code:

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("dgabbe/dgutils")
``` 

If you like how the bash prompt displays your current working directory, try my
[wdprompt](https://github.com/dgabbe/wdprompt) package to emulate this behavior.
